### 2021-07-09 src/paper/appendix_data.tex
Add model valiadation section. Restructure results.

Lastly, for the distribution of vaccinations every individual is assigned a vaccination
group and a vaccination rank from that group that creates a complete vaccination queue
over the population including 15\% that refuse to be vaccinated \citep{RKI2021}. The
vaccination groups are created to match the recommendations by the Ständige
Impfkommission \citep{VygenBonnet2020}.\footnote{We cover that teachers were prioritized
more than recommended by the commission.}% To cover that the Pfizer-BioNTech vaccine was later approved for younger age groups we
% put adolescents and children into two groups that follow after the general population.
% These groups do not become eligible within our simulation frame until June.

@@

\subsection{Number of Contacts}
\label{sub:number_of_contacts}

@@

In our empirical application we distinguish four groups of contact types: households,
education, work and other contacts.
% households
For households we assume that the individuals'
contacts in their households do not change over our estimation period.
% educ models
For nurseries, preschools and schools we implement vacations as announced by the German
federal states as well as school closures, emergency care and A / B schooling where only
one half of students attends every other week or day. For the moment we ignore that lack
of childcare leads working parents to stay home. An approximation of the share of contacts still taking place with the different school regulations can be found in Figure~\ref{fig:school_multiplier}.

@@

% work models
For our work models\footnote{We distinguish non-recurrent work contacts, daily work
    contacts and weekly work contacts.} we use the reductions in work mobility reported in
the Google Mobility Data \citep{Google2021} to calibrate our work policies. Reductions in
work contacts are not random but governed through a work contact priority where the
policy changes the threshold below which workers stay home. Figure
\ref{fig:work_multiplier} shows the share of workers that go to work in our model over
time.

@@

All shares of individuals who would take a rapid test if the conditions were met can be
seen in Figure~\ref{fig:rapid_test_demand}.\comment[id=J]{Talk about the interpretation
of each line.}

@@

>>>>

Lastly, for the distribution of vaccinations every individual is assigned a vaccination
group and a vaccination rank from that group that creates a complete vaccination queue
over the population including 15\% that refuse to be vaccinated \citep{RKI2021}. The
vaccination groups are created to match the recommendations by the Ständige
Impfkommission \citep{VygenBonnet2020}.\footnote{We cover that teachers were prioritized
more than recommended by the commission.}\comment[id=K]{Write how that plays out in our simulations for the different age groups.}

% To cover that the Pfizer-BioNTech vaccine was later approved for younger age groups we
% put adolescents and children into two groups that follow after the general population.
% These groups do not become eligible within our simulation frame until June.

% \begin{figure}[ht]   % vaccinations by age group
%   \centering
%   \includegraphics[width=\textwidth]{figures/results/figures/vaccinations/spring_baseline}
%   \caption{Simulated and Empirical Infections by Federal State}
%   \floatfoot{\noindent \textit{Note:} \textcolor{red}{To be written.}}
%   \label{fig:vaccinations_by_age_group}
% \end{figure}

@@

\subsection{Number of Contacts}
\label{subsec:data_number_of_contacts}

@@

In our empirical application\comment[id=K]{Improve language} we distinguish four groups
of contact types: households, education, work and other contacts.% households
For households we assume that the individuals'
contacts in their households do not change over our estimation period.
% educ models
For nurseries, preschools and schools we implement vacations as announced by the German
federal states as well as school closures, emergency care and A / B schooling where only
one half of students attends every other week or day. For the moment we ignore that lack
of childcare leads working parents to stay home. An approximation of the share of contacts still taking place with the different school regulations can be found in Figure~\ref{fig:school_multiplier}.

@@

% work
For our work contacts we use the reductions in work mobility reported in the Google
Mobility Data \citep{Google2021} to calibrate our work policies. Reductions in work
contacts are not random but governed through a work contact priority where the policy
changes the threshold below which workers stay home. Figure \ref{fig:work_multiplier}
shows the share of workers that go to work in our model over time.

@@

All shares of individuals who would take a rapid test if the conditions were met can be
seen in Figure~\ref{fig:rapid_test_demand}.

@@

 \comment[id=K]{J: Explain that we don't fit the share ever tested that well because our rapid test compliance is completely fixed. }

### 2021-07-09 src/paper/literature_review.tex
Add model valiadation section. Restructure results.

We build on two strands of literature: Recent extensions of the epidemiological SEIR
model and agent-based simulation models.\comment[id=K]{Write a sentence about the
\href{https://www.itwm.fraunhofer.de/de/presse-publikationen/presseinformationen/2021/2021-06-22_Dritte_Welle_Starker-Effekt-von-Schnelltests-an-Schulen.html}{Frauenhofer
paper} coming to similar conclusions: }

>>>>

We build on two strands of literature: Recent extensions of the epidemiological SEIR
model and agent-based simulation models.

### 2021-07-09 src/paper/model/number_of_contacts.tex
Add model valiadation section. Restructure results.

The number of random and recurrent contacts at the workplace, during leisure activities
and at home is calibrated with data provided by \citet{Mossong2008}. For details see
Section~\ref{sec:number_of_contacts}. In particular, we sample the number of contacts or
group sizes from empirical distributions that sometimes depend on age. It would also be
possible to use economic or other behavioral models to predict the number of contacts.

% Theoretically, each contact type can have its own infection probability. However, to
reduce the number of free parameters and thus avoid a potential over-fitting we only
estimate different infection probabilities for the areas work, school, preschool and
nurseries, households and other contacts.

>>>>

The number of random and recurrent contacts at the workplace, during leisure activities
and at home is calibrated with data provided by \citet{Mossong2008}. For details see
Section~\ref{subsec:data_number_of_contacts}. In particular, we sample the number of
contacts or group sizes from empirical distributions that sometimes depend on age. It
would also be possible to use economic or other behavioral models to predict the number
of contacts.

% Theoretically, each contact type can have its own infection probability. However, to
% reduce the number of free parameters and thus avoid a potential over-fitting we only
% estimate different infection probabilities for the areas work, school, preschool and
% nurseries, households and other contacts.

### 2021-07-09 src/paper/rapid_test_params.tex
Add model valiadation section. Restructure results.

According to the COSMO study \citep{Betsch2021a} 63\% would have been willing to take a
test in the round of 23rd of February 2021 when an acquaintance would have tested
positive. Since this is only asking for willingness not actual behavior and the demand
when meeting with friends is very likely lower, we take this as the upper bound of
private rapid test demand which is reached on May 4th. To cover that many people are
likely to have sought and done their first rapid test before the Easter holidays to meet
friends or family, we let the share of individuals doing rapid tests in that time
increase more rapidly than before and after. By end of March 25\% of individuals would do
a rapid test due to a private reason.

>>>>

According to the COSMO study \citep{Betsch2021a} 63\% would have been willing to take a
test in the round of 23rd of February 2021 when an acquaintance would have tested
positive. Since this is only asking for willingness not actual behavior and the demand
when meeting with friends is very likely lower, we take this as the upper bound of
private rapid test demand which is reached in the beginning of May. To cover that many
people are likely to have sought and done their first rapid test before the Easter
holidays to meet friends or family, we let the share of individuals doing rapid tests in
that time increase more rapidly than before and after. By end of March 25\% of
individuals would do a rapid test due to a private reason.

### 2021-07-09 src/paper/report.tex
Add model valiadation section. Restructure results.

At the core of our agent-based model are physical contacts between heterogeneous agents
(Figure~\ref{fig:model_contacts_infections}).\footnote{A detailed comparison with other
approaches  is relegated to Supplementary Material~\ref{sec:literature_review}. The
model most closely related to ours is described in \citet{Hinch2020}.} Each contact
between an infectious individual and somebody susceptible to the disease bears the risk
of transmitting the virus. Contacts occur in up to four networks: Within the household,
at work, at school, or in other settings (leisure activities, grocery shopping, medical
appointments, etc.). Some contacts recur regularly, others occur at random. Empirical
applications can take the population and household structure from census data and the
network-specific frequencies of contacts from diary data measuring contacts before the
pandemic \citep[e.g.][]{Mossong2008,Hoang2019}. Within each network, meeting frequencies
depend on age and geographical location (see Supplementary Material
Section~\ref{sub:number_of_contacts}).

>>>>

At the core of our agent-based model are physical contacts between heterogeneous agents
(Figure~\ref{fig:model_contacts_infections}).\footnote{A detailed comparison with other
approaches  is relegated to Supplementary Material~\ref{sec:literature_review}. The
model most closely related to ours is described in \citet{Hinch2020}.} Each contact
between an infectious individual and somebody susceptible to the disease bears the risk
of transmitting the virus. Contacts occur in up to four networks: Within the household,
at work, at school, or in other settings (leisure activities, grocery shopping, medical
appointments, etc.). Some contacts recur regularly, others occur at random. Empirical
applications can take the population and household structure from census data and the
network-specific frequencies of contacts from diary data measuring contacts before the
pandemic \citep[e.g.][]{Mossong2008,Hoang2019}. Within each network, meeting frequencies
depend on age and geographical location (see Supplementary Material
Section~\ref{subsec:data_number_of_contacts}).

### 2021-07-09 src/paper/results/fit.tex
Add model valiadation section. Restructure results.

\subsection{Simulated vs. Empirical Data}
\label{subsec:fit_results}

@@

\begin{figure}[ht]  % newly infected with single runs
  \centering
  \includegraphics[width=\textwidth]{figures/results/figures/scenario_comparisons/combined_fit/full_newly_infected_with_single_runs}
  \caption{Development of the Total Infections Over the Full Simulation Time Frame with
  Single Simulation Runs}
  \floatfoot{\noindent \textit{Note:} The figure shows the true weekly incidence rates
  per 100,000 people, including undetected cases. The mean infection rate is the thick
  blue line. Single simulation runs are plotted in lighter and thinner lines. The higher
  the mean incidence and the stronger the growth the more variance there is between
  simulation runs. We averaged over 30 simulation runs.}
  \label{fig:newly_infected_in_baseline}
\end{figure}

@@

\begin{figure}[ht]   % vaccinations by age group
  \centering
  \includegraphics[width=\textwidth]{figures/results/figures/vaccinations/spring_baseline}
  \caption{Simulated and Empirical Infections by Federal State}
  \floatfoot{\noindent \textit{Note:} \textcolor{red}{To be written.}}
  \label{fig:state_fit}
\end{figure}

>>>>

\subsection{Model Fit}
\label{subsec:fit_results}

@@

@@

### 2021-07-09 src/paper/results/scenarios.tex
Add model valiadation section. Restructure results.

\begin{figure}[ht] % Robustness Check
  \centering
  \begin{subfigure}[b]{.49\textwidth}
    \centering
    \includegraphics[width=0.9 \textwidth]{figures/results/figures/scenario_comparisons/robustness_check/full_new_known_case}
    \caption{Reported Cases}
    \label{fig:robustness_check_new_known_case}
  \end{subfigure}%
  \hfill
  \begin{subfigure}[b]{.49\textwidth}
    \centering
    \includegraphics[width=0.9 \textwidth]{figures/results/figures/scenario_comparisons/robustness_check/full_newly_infected}
    \caption{Total Cases}
    \label{fig:robustness_check_newly_infected}
  \end{subfigure}
  \caption{Robustness Check}
  \label{fig:robustness_check_detailed}
  \floatfoot{\noindent \textit{Note:} \textcolor{red}{To be written}}
\end{figure}

 \comment[id=K]{@Janos: Please add caption and description for the robustness check }

@@

>>>>

@@

 \comment[id=K]{Describe that random tests are more effective at detecting cases and that
 explains the bump in the random test scenario detection in the beginning. However, cases
 fall immediately more in the non-random scenario because the targeted demand for tests
 by household members leads to a much more efficient interruption of infection chains
 because we catch the household members very early in their infectious period.}
